AP/PA Tables ITHIM Global

### 2021-11-29 summary_tables_PA_AP.Rmd
Regen

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
io <- readRDS("results/multi_city/io.rds")

@@

```{r}
# high<- c(70, 25, 150,60)
# low<- c(40,15,100,40)
# l <- htmltools::tagList()
for (x in 1:length(cities)) {
  # print(cities[x])
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11] <- c("Baseline","Walking",
                                                        "Bicycling", "Driving",
                                                        "Motorcycling", 
                                                        "Public Transport")
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:`Public Transport`, factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
    geom_boxplot(outlier.shape = 8) + ggtitle(cities[x]) +
    labs(y = "Daily PM2.5 Concentration", x = "Scenarios") #+
  # +ylim(low[x],high[x])
  # yy <- ggplot() +
  #   geom_density(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
  #   ggtitle(cities[x]) +
  #   labs(y = "Daily PM2.5 Concentration", x = "Scenarios")
  print(y)
  #print(yy)
  # l[[i]] <- ggplotly(ggplot(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
  #   geom_boxplot(outlier.shape = 8) + ggtitle(cities[x]) +
  #   labs(y = "Daily PM2.5 Concentration", x = "Scenarios"))
  # print(ggplotly(yy))
}
```

@@

for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11]<-c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling", "Public Transport")
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc, Baseline:`Public Transport`, factor_key=TRUE)
  summary<- as.data.frame(data_long %>% group_by(scenario) %>% summarise('mean'=mean(pm_conc),'5th'=quantile(pm_conc, 0.05),'50th'=quantile(pm_conc, 0.5),'95th'=quantile(pm_conc, 0.9)))
  summary<- cbind(summary$scenario ,round(summary[,2:5], digits=1))
  summary$change_PM<- round(io[[cities[x]]]$outcomes$scenario_pm - io[[cities[x]]]$outcomes$scenario_pm[1], digits=2)
  names(summary)[1]<-"Scenario"
  print(kable(summary, caption= cities[x]))

@@

#trans_share<-c(22.5, 40.0, 22.5, 28.1) 
#pm_conc<- c(50, 18, 122, 47 )
city<-cities
#shares<- as.data.frame(cbind(city,as.numeric(io), pm_conc))
#names(shares)[2]<- "trans_share"

sl <- list()
for (x in 1:length(cities))
{
  modes<-names(unlist(io[[cities[x]]]$PM_emission_inventory))
  emissions<-as.data.frame(unlist(io[[cities[x]]]$PM_emission_inventory))
  city_emissions<-cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$PM_emission_inventory)`))
  names(city_emissions)[2]<- "emissions"
  select<- c("car", "motorcycle", "bus_driver", "truck", "big_truck")
  city_emissions$modes<- as.character(city_emissions$modes)
  city_emissions$modes[!(city_emissions$modes %in% select)]<- "other"
  summary<-city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2]<- cities[x]
  summary[[cities[x]]] <- round(summary[[cities[x]]]*100/sum(summary[[cities[x]]]), digits=1)
  summary<-as.data.frame(summary)
  summary[nrow(summary)+1,1] <- "Transport share"
  summary[nrow(summary),2]<- as.character(round(pm_trans_share[[cities[x]]] * 100))
  summary[nrow(summary)+1,1] <- "PM2.5 Conc"
  summary[nrow(summary),2] <- as.character(pm_conc_base[[cities[x]]])
  io[[cities[x]]]$summary_emission<- summary

@@

cl <- list()
for (city in cities)
{

@@

cl$Scenario <- c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling", "Public Transport")

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit=100
for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling", "Public Transport")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:`Public Transport`, factor_key=TRUE)
  y<-ggplot(data_long, aes(x=scenario, y=mmet, fill=scenario)) + geom_boxplot(outlier.shape = NA)+ ggtitle(cities[x])+ labs(y="Weekly MMET", x = "Scenarios")+  ylim(0, limit)
  print(y)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
for (x in 1:length(cities)) {
  names(io[[cities[x]]]$outcomes$mmets)[5:10] <- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key = TRUE)
  summary <- as.data.frame(data_long %>% group_by(scenario) %>% 
                             summarise('mean' = mean(mmet),
                                       '5th' = quantile(mmet, 0.05),
                                       '50th' = quantile(mmet, 0.5),
                                       '95th' = quantile(mmet, 0.9)))
  summary <- cbind(summary$scenario ,round(summary[,2:5], digits = 1))
  names(summary)[1] <- "Scenario"
  print(kable(summary, caption = cities[x]))

@@

cl <- list()
for (city in cities)
{

  td <- round(colMeans(io[[city]]$outcomes$mmets[,5:10], na.rm = T), 1) %>% as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)

@@

  # PM 2.5 table and plot
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11] <- c("Baseline","Walking",
                                                        "Bicycling", "Driving",
                                                        "Motorcycling", 
                                                        "Public Transport")
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:`Public Transport`, factor_key = TRUE)

@@

  # CO2
  td <- round(colSums(io[[cities[x]]]$outcomes$co2_conc, na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  #names(td) <- c('Scenario', cities[x])
  names(td) <- c('Scenario', 'CO2')
  td$Scenario <- c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling",
                   "Public Transport")

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  names(io[[cities[x]]]$outcomes$mmets)[5:10] <- c("Baseline","Walking",
                                                   "Bicycling", "Driving",
                                                   "Motorcycling", 
                                                   "Public Transport")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:`Public Transport`, factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) + geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly MMET", x = "Scenarios") + ylim(0, limit)
  print(y)

>>>>

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}
io <- readRDS("results/multi_city/io.rds")

@@

```{r}
# high<- c(70, 25, 150,60)
# low<- c(40,15,100,40)
# l <- htmltools::tagList()
for (x in 1:length(cities)) {
  # print(cities[x])
  # names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11] <- c("Baseline","Walking",
  #                                                       "Bicycling", "Driving",
  #                                                       "Motorcycling", 
  #                                                       "Public Transport")
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:9] <- c("Baseline", "Bicycling",
                                                        "Driving", "Public Transport")
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:`Public Transport`, factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
    geom_boxplot(outlier.shape = 8) + ggtitle(cities[x]) +
    labs(y = "Daily PM2.5 Concentration", x = "Scenarios") #+
  # +ylim(low[x],high[x])
  # yy <- ggplot() +
  #   geom_density(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
  #   ggtitle(cities[x]) +
  #   labs(y = "Daily PM2.5 Concentration", x = "Scenarios")
  print(y)
  #print(yy)
  # l[[i]] <- ggplotly(ggplot(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
  #   geom_boxplot(outlier.shape = 8) + ggtitle(cities[x]) +
  #   labs(y = "Daily PM2.5 Concentration", x = "Scenarios"))
  # print(ggplotly(yy))
}
```

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
data_long <- NA
summary <- NA
for (x in 1:length(cities)) {
  #names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11]<-c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling", "Public Transport")
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:9] <- c("Baseline", "Bicycling", 
                                                     "Driving", "Public Transport")
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:`Public Transport`, factor_key = TRUE)
  summary <- as.data.frame(data_long %>% group_by(scenario) %>%
                             summarise('mean' = mean(pm_conc),
                                       '5th' = quantile(pm_conc, 0.05),
                                       '50th' = quantile(pm_conc, 0.5),
                                       '95th' = quantile(pm_conc, 0.9)))
  summary <- cbind(summary$scenario ,round(summary[,2:5], digits = 1))
  summary$change_PM <- round(io[[cities[x]]]$outcomes$scenario_pm - io[[cities[x]]]$outcomes$scenario_pm[1], digits=2)
  names(summary)[1] <- "Scenario"
  print(kable(summary, caption = cities[x]))

@@

#trans_share<-c(22.5, 40.0, 22.5, 28.1) 
#pm_conc<- c(50, 18, 122, 47 )
city <- cities
#shares<- as.data.frame(cbind(city,as.numeric(io), pm_conc))
#names(shares)[2]<- "trans_share"

sl <- list()
for (x in 1:length(cities))
{
  modes <- names(unlist(io[[cities[x]]]$PM_emission_inventory))
  emissions <- as.data.frame(unlist(io[[cities[x]]]$PM_emission_inventory))
  city_emissions <- cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$PM_emission_inventory)`))
  names(city_emissions)[2] <- "emissions"
  select <- c("car", "motorcycle", "bus_driver", "truck", "big_truck")
  city_emissions$modes <- as.character(city_emissions$modes)
  city_emissions$modes[!(city_emissions$modes %in% select)] <- "other"
  summary <- city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2] <- cities[x]
  summary[[cities[x]]] <- round(summary[[cities[x]]]*100/sum(summary[[cities[x]]]), digits = 1)
  summary <- as.data.frame(summary)
  summary[nrow(summary) + 1,1] <- "Transport share"
  summary[nrow(summary),2] <- as.character(round(pm_trans_share[[cities[x]]] * 100))
  summary[nrow(summary) + 1,1] <- "PM2.5 Conc"
  summary[nrow(summary),2] <- as.character(pm_conc_base[[cities[x]]])
  io[[cities[x]]]$summary_emission <- summary

@@

cl <- list()
td <- NA
for (city in cities) {

@@

#cl$Scenario <- c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling", "Public Transport")
cl$Scenario <- c("Baseline", "Bicycling", "Driving", "Public Transport")

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  #names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling", "Public Transport")
  names(io[[cities[x]]]$outcomes$mmets)[5:8] <- c("Baseline", "Bicycling", 
                                                  "Driving", "Public Transport")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:`Public Transport`, factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) +
    geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly MMET", x = "Scenarios")+  ylim(0, limit)
  print(y)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
for (x in 1:length(cities)) {
  #names(io[[cities[x]]]$outcomes$mmets)[5:10] <- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  names(io[[cities[x]]]$outcomes$mmets)[5:8] <- c("baseline","bike_scen", 
                                                  "car_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key = TRUE)
  summary <- as.data.frame(data_long %>% group_by(scenario) %>% 
                             summarise('mean' = mean(mmet),
                                       '5th' = quantile(mmet, 0.05),
                                       '50th' = quantile(mmet, 0.5),
                                       '95th' = quantile(mmet, 0.9)))
  summary <- cbind(summary$scenario ,round(summary[,2:5], digits = 1))
  names(summary)[1] <- "Scenario"
  print(kable(summary, caption = cities[x]))

@@

cl <- list()
for (city in cities)
{
  #td <- round(colMeans(io[[city]]$outcomes$mmets[,5:10], na.rm = T), 1) %>%
  #  as.data.frame() %>% tibble::rownames_to_column()
  td <- round(colMeans(io[[city]]$outcomes$mmets[,5:8], na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)

@@

  # PM 2.5 table and plot
  # names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11] <- c("Baseline","Walking",
  #                                                       "Bicycling", "Driving",
  #                                                       "Motorcycling", 
  #                                                       "Public Transport")
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:9] <- c("Baseline",
                                                        "Bicycling", "Driving",
                                                        "Public Transport")

  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:`Public Transport`, factor_key = TRUE)

@@

  # CO2
  td <- round(colSums(io[[cities[x]]]$outcomes$co2_conc, na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  #names(td) <- c('Scenario', cities[x])
  names(td) <- c('Scenario', 'CO2')
  # td$Scenario <- c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling",
  #                  "Public Transport")
  td$Scenario <- c("Baseline", "Bicycling", "Driving", "Public Transport")

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  # names(io[[cities[x]]]$outcomes$mmets)[5:10] <- c("Baseline","Walking",
  #                                                  "Bicycling", "Driving",
  #                                                  "Motorcycling", 
  #                                                  "Public Transport")
  names(io[[cities[x]]]$outcomes$mmets)[5:8] <- c("Baseline",
                                                   "Bicycling", "Driving",
                                                   "Public Transport")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:`Public Transport`, factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) + geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly MMET", x = "Scenarios") + ylim(0, limit)
  print(y)
